### 2020-12-24 Draft.Rmd
Adding all relevant files

---
title: "Assignment 3 - Draft"
author: "Philipp Holz"
date: 'December 12, 2020'
output: 
  github_document:
    toc: true
    keep_html: true
bibliography: References.json

---

```{r libraries, include=FALSE}
# Loading the libraries ----
library(dplyr)
library(ggplot2)
library(scales)
library(lme4)
```

```{r data, eval=TRUE, include=FALSE}

# Data Wrangling -----
## Adding the Policy Data -----
### Read in the Data
policy_data <- read.csv("C:/Users/holzp/Desktop/RProject/PolicyData.csv")

### convert Date column to date format
policy_data$Date = as.Date(as.character(policy_data$Date), format = "%Y%m%d")

### create dataframe with only national level data
policy_data_countries <- policy_data %>% filter(Jurisdiction == "NAT_TOTAL")

### create dataframe with only national level of Germany, France, UK, Spain, Italy
policy_data_Europe <- policy_data_countries %>% filter(CountryCode == "DEU" |
                                                         CountryCode == "ITA" |
                                                         CountryCode == "FRA" |
                                                         CountryCode == "ESP" |
                                                         CountryCode == "GBR" |
                                                         CountryCode == "NLD" |
                                                         CountryCode == "BEL" |
                                                         CountryCode == "POL" |
                                                         CountryCode == "SWE" |
                                                         CountryCode == "AUT" |
                                                         CountryCode == "IRL" |
                                                         CountryCode == "DNK")

## Adding the Mobility Data ----
### Reading in the data
mobility_data <- read.csv("C:/Users/holzp/Desktop/RProject/MobilityData.csv")

### Add a column with an average of the change in sectors, excluding residential and parks

mobility_data <- mobility_data %>% mutate(avg_change = rowMeans(.[,c(6, 7, 9, 10)]))

### force recognition of the date format
mobility_data$date = as.Date(mobility_data$date, format = "%Y-%m-%d")

### Filter so that only country-level data remains
mobility_data_countries <- mobility_data %>% filter(sub.region.1 == "Total" & sub.region.2 == "Total")

### Create mobility data frame for Europe
mobility_data_Europe <- mobility_data_countries %>% filter(country == "Germany" |
                                                             country == "Italy" |
                                                             country == "France" |
                                                             country == "United Kingdom" |
                                                             country == "Spain" |
                                                             country == "Netherlands" |
                                                             country == "Belgium" |
                                                             country == "Poland" |
                                                             country == "Sweden" |
                                                             country == "Austria" |
                                                             country == "Denmark" |
                                                             country == "Ireland")

## Merging the Data into policyMobility_data_Europe ----
### renaming the date columns to match
names(mobility_data_Europe)[names(mobility_data_Europe)=="date"] <- "Date"
names(mobility_data_Europe)[names(mobility_data_Europe)=="country"] <- "CountryName"
names(mobility_data_Europe)[names(mobility_data_Europe)=="avg_change"] <- "MobilityIndex"

### Only selecting the columns that are interesting
mobility_data_Europe_small <- mobility_data_Europe %>% select(Date, CountryName, MobilityIndex)
policy_data_Europe_small <- policy_data_Europe %>% select(Date, CountryName, StringencyIndex)

### Merging policy and mobility data on date
policyMobility_data_Europe = mobility_data_Europe_small %>% 
  inner_join(policy_data_Europe_small, by = c("Date", "CountryName"))

## Adding a column with Compliance-index ----

policyMobility_data_Europe$ComplianceIndex <- 100 - (policyMobility_data_Europe$StringencyIndex + policyMobility_data_Europe$MobilityIndex)

### Rescaling the Compliance-index to assume values between 0 and 100

policyMobility_data_Europe$ComplianceIndex <- rescale(policyMobility_data_Europe$ComplianceIndex, to = c(0, 100))

```

# Introduction

The COVID-19-Pandemic is an ongoing challenge for policy-makers. Especially, because overcoming it is so dependent on the policy-compliance of each and every individual. However, how is the state of this policy-compliance in Europe? Does it differ across different countries and how does it evolve over time?

To find an answer to these questions, the following analysis will assess the following hypothesis.

H₀: There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.

Hₐ: There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.

This analysis combines data from the Google COVID-19 Community Mobility Reports [@COVID19CommunityMobility2020] and data from the the Oxford Policy Tracker [@haleOxfordCOVID19Government2020]. The Google Mobility Report charts "movement trends over time by geography, across different categories."[@COVID19CommunityMobility2020] For the sake of this analysis the movement trends of the categories retail and recreation, supermarkets and pharmacies, public transport and workplaces were included and averaged without weighting. The Stringency Index was obtained from the Oxford Policy Tracker and records information on "the strictness of 'lockdown style' policies that primarily restrict people's behaviour."[@haleOxfordCOVID19Government2020]

Countries included in the analysis were chosen based on their membership to the EU (including the United Kingdom) and their GDP.

The following diagram shows how in March, April and May lock style policies were introduced and how mobility was reduced in concordance in almost all of the countries assessed. However, beginning immediately from there on, mobility started to increase again, with the gap between policy stringency and observed mobility-reduction widening. Note that policy stringency is on the left y-axis and mobility changes on the right. The scale of policy stringency is reversed for better comparability.

```{r faceted plot Stringency and Mobility, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center"}
## Create a faceted plot with Stringency and Mobility for European Countries ----

ggplot(data = policyMobility_data_Europe) +
  geom_line(aes(x = Date, y = StringencyIndex), color = "black", linetype = "longdash", size = 0.5) +
  geom_smooth(aes(x = Date, y = -1*MobilityIndex), method = "loess", span = 1/10, 
              se = FALSE, size = 0.5, color = "black", linetype = "solid") +
  facet_wrap(~CountryName) +
  xlab("Month") +
  scale_x_date(breaks = date_breaks("3 months"),
               labels = date_format("%b\n%Y")) +
  scale_y_reverse(name = "Policy Stringency Index (dashed line)",
                  sec.axis = sec_axis(~.*-1, name = "Mobility %-change vs Baseline (solid line)")) +
  theme(
    axis.title.x = element_text(vjust = 0.5),
    axis.title.y = element_text(color = "black", size=12, vjust = 3),
    axis.title.y.right = element_text(color = "black", size=12, vjust = 3)
  ) +
  geom_hline(yintercept = 0, color = "black", size = 0.5) +
  ggtitle("Development of Policy Stringency and Mobility Reduction in Europe")
```

# Variation in Policy-Compliance

In order to build our model, we can make a preliminary, bivariate analysis that shows the variance of policy compliance across different European countries.

For this step, we can approximate policy-compliance as the difference between the level of policy-stringency and the observed reduction in mobility. The boxplot shows us that, indeed, the levels of policy compliance among European countries differ.

```{r boxplot compliance, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center"}
## Create a Boxplot of Compliance by Country ----
ggplot(data = policyMobility_data_Europe, aes(x = CountryName, y = ComplianceIndex)) +
  geom_boxplot() +
  xlab("Country") +
  ylab("Policy Compliance Index") +
  ggtitle("Policy Compliance in Europe") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) 
```

Additionally, as we want to assess the change of policy compliance across time in Europe, we can fit a linear regression line to the compliance data. This shows us that in all of the European countries analyzed, compliance with mobility-reducing-policies has reduced.

```{r facetted plot compliance, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center"}
## Create a faceted plot with Compliance for European Countries ----
ggplot(policyMobility_data_Europe) +
  geom_smooth(aes(x = Date, y = ComplianceIndex), method = "loess", se = FALSE, span = 1/10, 
              color = "black", linetype = "solid", size = 0.1) +
  geom_smooth(aes(x = Date, y = ComplianceIndex), method = "lm", se = FALSE, 
              color = "black", linetype = "solid", size = 1) + 
  facet_wrap(~CountryName) +
  xlab("Month") +
  scale_x_date(breaks = date_breaks("3 months"),
               labels = date_format("%b\n%Y")) +
  scale_y_continuous(name = "Policy Compliance Index") +
  theme(
    axis.title.y = element_text(color = "black", size=12, vjust = 3),
    axis.title.x = element_text(size=12, vjust = 0.5)
    ) +
  ggtitle("Policy Compliance in Europe Across Time")
```

However, as initially stated, approximating policy-compliance as the difference between the level of policy-stringency and the observed reduction in mobility cannot be more than an approximation. When plotted across countries it shows a difference in means, and when plotted across time it shows a difference in trend.

An alternative measure of policy-compliance comes to mind, that accounts for measurement-errors and country-level differences. This alternative measure would be informed by the degree to which the mobility-reduction of a given population over time can be predicted by policy-stringency. As will be shown in more detail below, such a model is a hierarchical random-effect model.

# Modelling
## Linear Non-Hierachical Model

The following non-hierarchical model predicts the Mobility Index as the dependent variable, with the Stringency Index, Date and Country as the independent variables.

Predicted Mobility Index = β₀ + β₁ × Stringency Index + β₂ × Date + β₃ × Country + ε

It yields the following result. The continuous variables Stringency Index and Date are both statistically significant at the 0.05 level. They show that with increased stringency the mobility decreases, while a later date is associated with an increased mobility. Also all expressions of the categorical variable Country are significant at the 0.05 level, with the exception of the United Kingdom.

The United Kingdom being a non-significant exception in the non-hierarchical linear model is an interesting case, as we could observe from our previous diagram with the compliance-approximation that, on a country-level with a random intercept and a random slope, the linear regression line fitted the United Kingdom data exceptionally *well*. Thus, we require

| Variable                  | Coefficient | Std. Error | p-value      |
| ------------------------- | ----------- | ---------- | ------------ |
| Stringency Index          | -7.045e-01  | 9.107e-03  | < 2e-16 ***  |
| Date                      | 6.122e-02   | 1.993e-03  | < 2e-16 ***  |
| Belgium                   | 2.463e+00   | 8.466e-01  | 0.003649 **  |
| Denmark                   | 1.066e+01   | 8.430e-01  | < 2e-16 ***  |
| France                    | 5.306e+00   | 8.474e-01  | 4.25e-10 *** |
| Germany                   | 1.208e+01   | 8.445e-01  | < 2e-16 ***  |
| Ireland                   | 2.999e+00   | 8.523e-01  | 0.000439 *** |
| Italy                     | 5.026e+00   | 8.544e-01  | 4.39e-09 *** |
| Netherlands               | 5.089e+00   | 8.564e-01  | 3.09e-09 *** |
| Poland                    | 7.011e+00   | 8.443e-01  | < 2e-16 ***  |
| Spain                     | 2.109e+00   | 8.523e-01  | 0.013401 *   |
| Sweden                    | 1.117e+01   | 8.431e-01  | < 2e-16 ***  |
| United Kingdom            | -2.997e-01  | 8.499e-01  | 0.724393     |

# References

### 2020-12-24 Script.R

@@ -1,0 +1,248 @@
+# Loading the libraries ----
+library(dplyr)
+library(ggplot2)
+library(scales)
+library(lme4)
+library(broom.mixed)
+library(plotly)
+library(reshape2)
+
+# Data Wrangling -----
+## Adding the Policy Data -----
+### Read in the Data
+policy_data <- read.csv("PolicyData.csv")
+
+### convert Date column to date format
+policy_data$Date = as.Date(as.character(policy_data$Date), format = "%Y%m%d")
+
+### create dataframe with only national level data
+policy_data_countries <- policy_data %>% filter(Jurisdiction == "NAT_TOTAL")
+
+### create dataframe with only national level of Germany, France, UK, Spain, Italy
+policy_data_Europe <- policy_data_countries %>% filter(CountryCode == "DEU" |
+                                                         CountryCode == "ITA" |
+                                                         CountryCode == "FRA" |
+                                                         CountryCode == "ESP" |
+                                                         CountryCode == "GBR" |
+                                                         CountryCode == "NLD" |
+                                                         CountryCode == "BEL" |
+                                                         CountryCode == "POL" |
+                                                         CountryCode == "SWE" |
+                                                         CountryCode == "AUT" |
+                                                         CountryCode == "IRL" |
+                                                         CountryCode == "DNK")
+
+
+## Adding the Mobility Data ----
+### Reading in the data
+mobility_data <- read.csv("MobilityData.csv")
+
+### Add a column with an average of the change in sectors, excluding residential and parks
+
+mobility_data <- mobility_data %>% mutate(avg_change = rowMeans(.[,c(6, 7, 9, 10)]))
+
+### force recognition of the date format
+mobility_data$date = as.Date(mobility_data$date, format = "%Y-%m-%d")
+
+### Filter so that only country-level data remains
+mobility_data_countries <- mobility_data %>% filter(sub.region.1 == "Total" & sub.region.2 == "Total")
+
+### Create mobility data frame for Europe
+mobility_data_Europe <- mobility_data_countries %>% filter(country == "Germany" |
[…]

### 2020-12-24 Script.R
Data Wrangling for Cases Data, Adding the Trends Dataset

@@ -6,6 +6,7 @@ library(lme4)
 library(broom.mixed)
 library(plotly)
 library(reshape2)
+library(utils)
 
 # Data Wrangling -----
 ## Adding the Policy Data -----
@@ -31,6 +32,9 @@ policy_data_Europe <- policy_data_countries %>% filter(CountryCode == "DEU" |
                                                          CountryCode == "AUT" |
                                                          CountryCode == "IRL" |
                                                          CountryCode == "DNK")
+
+### Only selecting the columns that are interesting
+policy_data_Europe_small <- policy_data_Europe %>% select(Date, CountryName, StringencyIndex)
 
 
 ## Adding the Mobility Data ----
@@ -61,20 +65,55 @@ mobility_data_Europe <- mobility_data_countries %>% filter(country == "Germany" 
                                                              country == "Denmark" |
                                                              country == "Ireland")
 
-## Merging the Data into policyMobility_data_Europe ----
 ### renaming the date columns to match
 names(mobility_data_Europe)[names(mobility_data_Europe)=="date"] <- "Date"
 names(mobility_data_Europe)[names(mobility_data_Europe)=="country"] <- "CountryName"
 names(mobility_data_Europe)[names(mobility_data_Europe)=="avg_change"] <- "MobilityIndex"
 
-### Only selecting the columns that are interesting
+### Only selecting relevant data
 mobility_data_Europe_small <- mobility_data_Europe %>% select(Date, CountryName, MobilityIndex)
-policy_data_Europe_small <- policy_data_Europe %>% select(Date, CountryName, StringencyIndex)
 
-### Merging policy and mobility data on date
-policyMobility_data_Europe = mobility_data_Europe_small %>% 
-  inner_join(policy_data_Europe_small, by = c("Date", "CountryName"))
 
+## Adding the Cases Data ----
+
+###read the Dataset sheet in
+cases_data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM")
+cases_data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
+
+### renaming the date and countries columns to match
+names(cases_data)[names(cases_data)=="dateRep"] <- "Date"
+names(cases_data)[names(cases_data)=="countriesAndTerritories"] <- "CountryName"
+
+### Forcing Date format
[…]

### 2020-12-24 Script.R
Adding datawrangling for cases_data. New conjoined dataset is data

@@ -77,7 +77,6 @@ mobility_data_Europe_small <- mobility_data_Europe %>% select(Date, CountryName,
 ## Adding the Cases Data ----
 
 ###read the Dataset sheet in
-cases_data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM")
 cases_data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
 
 ### renaming the date and countries columns to match
@@ -102,14 +101,17 @@ cases_data_Europe <- cases_data %>% filter(CountryName == "Germany" |
                                              CountryName == "Denmark")
 
 ### Changing United_Kingdom to United Kingdom
-rename <- c(United_Kingdom="United Kingdom")
+rename <- c(United_Kingdom="United Kingdom", Germany="Germany", Italy="Italy",
+            France="France", Spain="Spain", Netherlands="Netherlands", Belgium="Belgium",
+            Poland="Poland", Sweden="Sweden", Ireland="Ireland", Austria="Austria",
+            Denmark="Denmark")
 
 cases_data_Europe$CountryName <- as.character(rename[cases_data_Europe$CountryName])
 
 ### Only selecting the columns that are interesting
 cases_data_Europe_small <- cases_data_Europe %>% select(Date, CountryName, notification_rate_per_100000_population_14.days)
 
-## Merging policy mobility trends and cases data on date and country
+## Merging policy mobility trends and cases data on date and country ----
 
 data = policy_data_Europe_small %>% 
   full_join(mobility_data_Europe_small, by = c("Date", "CountryName")) %>%

### 2020-12-24 Script.R
Adding trends data and including Austria, Denmark and Ireland in Countries

@@ -111,11 +111,24 @@ cases_data_Europe$CountryName <- as.character(rename[cases_data_Europe$CountryNa
 ### Only selecting the columns that are interesting
 cases_data_Europe_small <- cases_data_Europe %>% select(Date, CountryName, notification_rate_per_100000_population_14.days)
 
+## Adding the Trends Data ----
+trends_data <- read.csv("GoogleTrends.csv", sep = ";")
+
+### Forcing correct date format
+trends_data$Date = as.Date(trends_data$Date, format = "%d.%m.%Y")+1
+
+## Renaming the Sum column to Publicity
+names(trends_data)[names(trends_data)=="Sum"] <- "Publicity"
+
+## Only selecting the columns that are interesting
+trends_data <- trends_data %>% select(Date, CountryName, Publicity)
+
 ## Merging policy mobility trends and cases data on date and country ----
 
 data = policy_data_Europe_small %>% 
   full_join(mobility_data_Europe_small, by = c("Date", "CountryName")) %>%
-  full_join(cases_data_Europe_small, by = c("Date", "CountryName"))
+  full_join(cases_data_Europe_small, by = c("Date", "CountryName")) %>%
+  full_join(trends_data, by = c("Date", "CountryName"))
 
 ## Adding a column with Compliance-index ----
 

### 2020-12-24 Draft.Rmd
Compliance Index added, and policyMobility_data_Europe Dataframe renamed to just data. Rmd draft updated from previous version with MobilityIndex as the dependent variable

@@
 ---
-title: "Assignment 3 - Draft"
+title: "COVID-19 Policy-Compliance in Europe"
 author: "Philipp Holz"
-date: 'December 12, 2020'
+date: 'December 24, 2020'
 output: 
@@
 library(lme4)
+library(broom.mixed)
+library(plotly)
+library(reshape2)
+library(utils)
 ```
@@
 ```{r data, eval=TRUE, include=FALSE}
-
 # Data Wrangling -----
@@
 ### Read in the Data
-policy_data <- read.csv("C:/Users/holzp/Desktop/RProject/PolicyData.csv")
+policy_data <- read.csv("PolicyData.csv")
 
@@
 
+### Only selecting the columns that are interesting
+policy_data_Europe_small <- policy_data_Europe %>% select(Date, CountryName, StringencyIndex)
+
 ## Adding the Mobility Data ----
 ### Reading in the data
-mobility_data <- read.csv("C:/Users/holzp/Desktop/RProject/MobilityData.csv")
+mobility_data <- read.csv("MobilityData.csv")
 
@@
 
-## Merging the Data into policyMobility_data_Europe ----
 ### renaming the date columns to match
@@
 
+### Only selecting relevant data
+mobility_data_Europe_small <- mobility_data_Europe %>% select(Date, CountryName, MobilityIndex)
+
+## Adding the Cases Data ----
+
+###read the Dataset sheet in
+cases_data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
+
+### renaming the date and countries columns to match
+names(cases_data)[names(cases_data)=="dateRep"] <- "Date"
+names(cases_data)[names(cases_data)=="countriesAndTerritories"] <- "CountryName"
+
+### Forcing Date format
+cases_data$Date = as.Date(as.character(cases_data$Date), format = "%d/%m/%Y")
+
+### create dataframe with only national level of Germany, France, UK, Spain, Italy
+cases_data_Europe <- cases_data %>% filter(CountryName == "Germany" |
+                                             CountryName == "Italy" |
+                                             CountryName == "France" |
+                                             CountryName == "Spain" |
+                                             CountryName == "United_Kingdom" |
+                                             CountryName == "Netherlands" |
+                                             CountryName == "Belgium" |
+                                             CountryName == "Poland" |
+                                             CountryName == "Sweden" |
+                                             CountryName == "Ireland" |
+                                             CountryName == "Austria" |
+                                             CountryName == "Denmark")
+
+### Changing United_Kingdom to United Kingdom
+rename <- c(United_Kingdom="United Kingdom", Germany="Germany", Italy="Italy",
+            France="France", Spain="Spain", Netherlands="Netherlands", Belgium="Belgium",
+            Poland="Poland", Sweden="Sweden", Ireland="Ireland", Austria="Austria",
+            Denmark="Denmark")
+
+cases_data_Europe$CountryName <- as.character(rename[cases_data_Europe$CountryName])
+
 ### Only selecting the columns that are interesting
-mobility_data_Europe_small <- mobility_data_Europe %>% select(Date, CountryName, MobilityIndex)
-policy_data_Europe_small <- policy_data_Europe %>% select(Date, CountryName, StringencyIndex)
+cases_data_Europe_small <- cases_data_Europe %>% select(Date, CountryName, notification_rate_per_100000_population_14.days)
 
-### Merging policy and mobility data on date
-policyMobility_data_Europe = mobility_data_Europe_small %>% 
-  inner_join(policy_data_Europe_small, by = c("Date", "CountryName"))
+## Adding the Trends Data ----
+trends_data <- read.csv("GoogleTrends.csv", sep = ";")
+
+### Forcing correct date format
+trends_data$Date = as.Date(trends_data$Date, format = "%d.%m.%Y")+1
+
+## Renaming the Sum column to Publicity
+names(trends_data)[names(trends_data)=="Sum"] <- "Publicity"
+
+## Only selecting the columns that are interesting
+trends_data <- trends_data %>% select(Date, CountryName, Publicity)
+
+## Merging policy mobility trends and cases data on date and country ----
+
+data = policy_data_Europe_small %>% 
+  full_join(mobility_data_Europe_small, by = c("Date", "CountryName")) %>%
+  full_join(cases_data_Europe_small, by = c("Date", "CountryName")) %>%
+  full_join(trends_data, by = c("Date", "CountryName"))
 
@@
 
-policyMobility_data_Europe$ComplianceIndex <- 100 - (policyMobility_data_Europe$StringencyIndex + policyMobility_data_Europe$MobilityIndex)
+data$ComplianceIndex <- 100 - (data$StringencyIndex + data$MobilityIndex)
 
@@
 
-policyMobility_data_Europe$ComplianceIndex <- rescale(policyMobility_data_Europe$ComplianceIndex, to = c(0, 100))
+data$ComplianceIndex <- rescale(data$ComplianceIndex, to = c(0, 100))
 
@@
 
-ggplot(data = policyMobility_data_Europe) +
+ggplot(data = data) +
   geom_line(aes(x = Date, y = StringencyIndex), color = "black", linetype = "longdash", size = 0.5) +
@@
   ggtitle("Development of Policy Stringency and Mobility Reduction in Europe")
+
 ```
@@
 
-For this step, we can approximate policy-compliance as the difference between the level of policy-stringency and the observed reduction in mobility.
+For this analysis, policy-compliance is approximated as the difference between the level of policy-stringency and the observed reduction in mobility.
+
+`Compliance = 100 - (Policy Stringency Index - %-change in Mobility)`
+
 The boxplot shows us that, indeed, the levels of policy compliance among European countries differ.
@@
 ## Create a Boxplot of Compliance by Country ----
-ggplot(data = policyMobility_data_Europe, aes(x = CountryName, y = ComplianceIndex)) +
+ggplot(data = data, aes(x = CountryName, y = ComplianceIndex)) +
   geom_boxplot() +
@@
 ## Create a faceted plot with Compliance for European Countries ----
-ggplot(policyMobility_data_Europe) +
+ggplot(data) +
   geom_smooth(aes(x = Date, y = ComplianceIndex), method = "loess", se = FALSE, span = 1/10, 
@@
 
-However, as initially stated, approximating policy-compliance as the difference between the level of policy-stringency and the observed reduction in mobility cannot be more than an approximation.
-When plotted across countries it shows a difference in means, and when plotted across time it shows a difference in trend.
-
-An alternative measure of policy-compliance comes to mind, that accounts for measurement-errors and country-level differences.
-This alternative measure would be informed by the degree to which the mobility-reduction of a given population over time can be predicted by policy-stringency.
-As will be shown in more detail below, such a model is a hierarchical random-effect model.
-
 # Modelling
@@
 
-Predicted Mobility Index = β₀ + β₁ × Stringency Index + β₂ × Date + β₃ × Country + ε
+`Compliance Index = β₀ + β₁ × Date + β₂ × Country + β₃ × Publicity + β₄ × Cases per 100.000 per 14 days + ε`
+
+THE FOLLOWING MUST BE UPDATED
 

### 2020-12-24 Script.R

@@ -132,20 +132,17 @@ data = policy_data_Europe_small %>%
 
 ## Adding a column with Compliance-index ----
 
-policyMobility_data_Europe$ComplianceIndex <- 100 - (policyMobility_data_Europe$StringencyIndex + policyMobility_data_Europe$MobilityIndex)
+data$ComplianceIndex <- 100 - (data$StringencyIndex + data$MobilityIndex)
 
 ### Rescaling the Compliance-index to assume values between 0 and 100
 
-policyMobility_data_Europe$ComplianceIndex <- rescale(policyMobility_data_Europe$ComplianceIndex, to = c(0, 100))
+data$ComplianceIndex <- rescale(data$ComplianceIndex, to = c(0, 100))
 
 
 # Explorative Data Visualization ----
-## Create a Boxplot of Mobility by Country ----
-ggplot(data = policyMobility_data_Europe, aes(x = CountryName, y = MobilityIndex)) +
-  geom_boxplot()
 
 ## Create a Boxplot of Compliance by Country ----
-ggplot(data = policyMobility_data_Europe, aes(x = CountryName, y = ComplianceIndex)) +
+ggplot(data = data, aes(x = CountryName, y = ComplianceIndex)) +
   geom_boxplot() +
   xlab("Country") +
   ylab("Policy Compliance Index") +
@@ -154,7 +151,7 @@ ggplot(data = policyMobility_data_Europe, aes(x = CountryName, y = ComplianceInd
 
 ## Create a faceted plot with Stringency and Mobility for European Countries ----
 
-ggplot(data = policyMobility_data_Europe) +
+ggplot(data = data) +
   geom_line(aes(x = Date, y = StringencyIndex), color = "black", linetype = "longdash", size = 0.5) +
   geom_smooth(aes(x = Date, y = -1*MobilityIndex), method = "loess", span = 1/10, 
               se = FALSE, size = 0.5, color = "black", linetype = "solid") +
@@ -173,7 +170,7 @@ ggplot(data = policyMobility_data_Europe) +
   ggtitle("Development of Policy Stringency and Mobility Reduction in Europe")
 
 ## Create a faceted plot with Compliance for European Countries ----
-ggplot(policyMobility_data_Europe) +
+ggplot(data) +
   geom_smooth(aes(x = Date, y = ComplianceIndex), method = "loess", se = FALSE, span = 1/10, 
               color = "black", linetype = "solid", size = 0.1) +
[…]

### 2020-12-24 Draft.Rmd
Trying to get automatic and nice regression table output with texreg, however this needs improvement

@@
 library(utils)
+library(texreg)
+library(stargazer)
 ```
@@
 
+```{r echo=FALSE, results="asis"}
+
+report_regression <- function(model, ...){
+  if(knitr::is_html_output()){
+    require(texreg)
+    htmlreg(model, custom.note="%stars. htmlreg", ...)
+  } else if(knitr::is_latex_output()){
+    require(stargazer)
+    stargazer(model, notes="stargazer html", ...)
+  } else {
+   print("This only works with latex and html output") 
+  }
+}
+
+lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)
+
+report_regression(lm1)
+```
+
 THE FOLLOWING MUST BE UPDATED

### 2020-12-24 Script.R

@@ -189,9 +189,21 @@ ggplot(data) +
 # Modelling ----
 
 ## Non-hierarchical model ----
-lm(data = data, MobilityIndex ~ StringencyIndex + CountryName + Date)
+lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days)
 
-summary(lm(data = data, MobilityIndex ~ StringencyIndex + CountryName + Date))
+summary(lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days))
+
+### Creating nice regression table output
+lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)
+
+#### Modify htmlreg arguments in order to improve table output
+table <- texreg::htmlreg(lm1, custom.note="%stars. htmlreg")
+
+tempDir <- tempfile()
+dir.create(tempDir)
+htmlFile <- file.path(tempDir, "test.html")
+writeLines(table, htmlFile)
+rstudioapi::viewer(htmlFile)
 
 ### Visualising different predicted intercepts and different slopes
 ggplot(data = augment(lm(data = data, 

### 2020-12-24 Draft.Rmd
Automated Regression table output in html

--- 2020-12-24 Draft.Rmd
@@
 
-THE FOLLOWING MUST BE UPDATED
-
 It yields the following result.
@@
 
+```{r Regression Table, echo=FALSE, results="asis", fig.align='center'}
+
+# Fit the model
+lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)
+
+# Generate regression table
+texreg::htmlreg(lm1, single.row = TRUE, 
+#                         custom.header = list("Model Results" = 1),
+#                         model.names = c("My name 1", "My name 2"), 
+                         custom.coef.names = c("Intercept", "Date", "Publicity",
+                                               "Cases/100,000/14 Days",
+                                               "Belgium",
+                                               "Denmark",
+                                               "France",
+                                               "Germany",
+                                               "Ireland",
+                                               "Italy",
+                                               "Netherlands",
+                                               "Poland",
+                                               "Spain",
+                                               "Sweden",
+                                               "United Kingdom"),
+                          bold = 0.05,
+                          center = TRUE,
+                          caption = "Regression Table"
+                         )
+```
+
 The United Kingdom being a non-significant exception in the non-hierarchical linear model is an interesting case, as we could observe from our previous diagram with the compliance-approximation that, on a country-level with a random intercept and a random slope, the linear regression line fitted the United Kingdom data exceptionally *well*.
 Thus, we require
+
+THIS TABLE WILL BE UPDATED BEFORE FINAL SUBMISSION
 

### 2020-12-24 Script.R

@@ -197,7 +197,27 @@ summary(lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification
 lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)
 
 #### Modify htmlreg arguments in order to improve table output
-table <- texreg::htmlreg(lm1, custom.note="%stars. htmlreg")
+#### Then insert the texreg statement in Rmd
+table <- texreg::htmlreg(lm1, single.row = TRUE, 
+#                         custom.header = list("Model Results" = 1),
+#                         model.names = c("My name 1", "My name 2"), 
+                         custom.coef.names = c("Intercept", "Date", "Publicity",
+                                               "Cases/100,000/14 Days",
+                                               "Belgium",
+                                               "Denmark",
+                                               "France",
+                                               "Germany",
+                                               "Ireland",
+                                               "Italy",
+                                               "Netherlands",
+                                               "Poland",
+                                               "Spain",
+                                               "Sweden",
+                                               "United Kingdom"),
+                          bold = 0.05,
+                          center = TRUE,
+                          caption = "Regression Table"
+                         )
 
 tempDir <- tempfile()
 dir.create(tempDir)

### 2020-12-24 Draft.Rmd
Changed html to pdf output

@@
 date: 'December 24, 2020'
-output:
-  github_document:
-    toc: true
-    keep_html: true
+output: pdf_document
 bibliography: References.json
@@
 
-H₀: There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.
+H(null): There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.
 
-Hₐ: There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.
+H(alternative): There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.
 
@@
 
-`Compliance Index = β₀ + β₁ × Date + β₂ × Country + β₃ × Publicity + β₄ × Cases per 100.000 per 14 days + ε`
-
 It yields the following result.
@@
 # Generate regression table
-texreg::htmlreg(lm1, single.row = TRUE, 
+texreg::texreg(lm1, single.row = TRUE, 
 #                         custom.header = list("Model Results" = 1),

### 2020-12-25 Draft.Rmd
Added Latex version of regression formula and new plot showing predicted values for policy compliance in different european countries

@@
 date: 'December 24, 2020'
-output: pdf_document
+output: 
+  pdf_document:
+    toc: true
+    latex_engine: xelatex
 bibliography: References.json
@@
 
+\begin{equation}
+{Compliance Index} = {\beta}_0 + {\beta}_1 * {Date} + {\beta}_2 * {Country} + {\beta}_3 * {Publicity} + {\beta}_4 * {Cases/100.000/14 days} + {\epsilon}
+\end{equation}
+
 It yields the following result.
-The continuous variables Stringency Index and Date are both statistically significant at the 0.05 level.
-They show that with increased stringency the mobility decreases, while a later date is associated with an increased mobility.
-Also all expressions of the categorical variable Country are significant at the 0.05 level, with the exception of the United Kingdom.
+Except for Date, non of the continuous variables Publicity and Cases/100.000/14 Days are statistically significant.
+Date is statistically significant at the 0.05 level.
+It's coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases by 0.07 points each day.
 
-```{r Regression Table, echo=FALSE, results="asis", fig.align='center'}
+With Country as the categorical variable, all expressions are statistically significant at the 0.05 level, with the exception of Belgium, Ireland, the Netherlands and the United Kingdom, when compared to Austria as the reference category.
+The adjusted R² indicates that the model explains 29% of the observed variance.
+
+```{r Regression Table, echo=FALSE, fig.align='center', results="asis"}
 
@@
 
-The United Kingdom being a non-significant exception in the non-hierarchical linear model is an interesting case, as we could observe from our previous diagram with the compliance-approximation that, on a country-level with a random intercept and a random slope, the linear regression line fitted the United Kingdom data exceptionally *well*.
-Thus, we require
+## Linear Multi-Level Model
 
-THIS TABLE WILL BE UPDATED BEFORE FINAL SUBMISSION
+However, when plotting the fitted values from the non-hierarchical linear model by country, we can observe different discrete levels of compliance by date, e.g.
+with Austria showing much higher levels of compliance than Germany and Sweden.
 
-| Variable                  | Coefficient | Std. Error | p-value      |
-| ------------------------- | ----------- | ---------- | ------------ |
-| Stringency Index          | -7.045e-01  | 9.107e-03  | < 2e-16 ***  |
-| Date                      | 6.122e-02   | 1.993e-03  | < 2e-16 ***  |
-| Belgium                   | 2.463e+00   | 8.466e-01  | 0.003649 **  |
-| Denmark                   | 1.066e+01   | 8.430e-01  | < 2e-16 ***  |
-| France                    | 5.306e+00   | 8.474e-01  | 4.25e-10 *** |
-| Germany                   | 1.208e+01   | 8.445e-01  | < 2e-16 ***  |
-| Ireland                   | 2.999e+00   | 8.523e-01  | 0.000439 *** |
-| Italy                     | 5.026e+00   | 8.544e-01  | 4.39e-09 *** |
-| Netherlands               | 5.089e+00   | 8.564e-01  | 3.09e-09 *** |
-| Poland                    | 7.011e+00   | 8.443e-01  | < 2e-16 ***  |
-| Spain                     | 2.109e+00   | 8.523e-01  | 0.013401 *   |
-| Sweden                    | 1.117e+01   | 8.431e-01  | < 2e-16 ***  |
-| United Kingdom            | -2.997e-01  | 8.499e-01  | 0.724393     |
+```{r Linear model predictions by country, echo=FALSE, fig.align='center', message=FALSE, warning=FALSE}
+### Visualising different predicted intercepts and different slopes
+ggplot(data = augment(lm(data = data, 
+                         ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days)),
+       aes(x = Date, y = ComplianceIndex, color = CountryName))  +
+  geom_smooth(aes(y = .fitted), method = "lm", se = FALSE) +
+  xlab("Month") +
+  scale_x_date(breaks = date_breaks("3 months"),
+               labels = date_format("%b\n%Y")) +
+  scale_y_continuous(name = "Policy Compliance Index") +
+  theme(
+    axis.title.y = element_text(color = "black", size=12, vjust = 3),
+    axis.title.x = element_text(size=12, vjust = 0.5)
+    ) +
+  ggtitle("Model Predictions for Policy Compliance in Europe Across Time")
+```
+
+This suggests creating a hierarchical model with a random intercept for country in order to improve model fit.
 

### 2020-12-25 Script.R

@@ -8,6 +8,11 @@ library(plotly)
 library(reshape2)
 library(utils)
 
+# Hypothesis
+#H₀: There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.
+
+#Hₐ: There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.
+
 # Data Wrangling -----
 ## Adding the Policy Data -----
 ### Read in the Data
@@ -189,6 +194,10 @@ ggplot(data) +
 # Modelling ----
 
 ## Non-hierarchical model ----
+
+`Compliance Index = β₀ + β₁ × Date + β₂ × Country + β₃ × Publicity + β₄ × Cases per 100.000 per 14 days + ε`
+
+
 lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days)
 
 summary(lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days))

### 2020-12-25 Draft.Rmd
Improved fonts in Hypotheses, formulas and plots

@@
 ---
+
+```{r, echo=FALSE, message = FALSE}
+knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = FALSE, dev = "cairo_pdf")
+```
 
@@
 library(stargazer)
+library(extrafont)
+loadfonts()
 ```
@@
 
-H(null): There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.
+H\textsubscript{0}: There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.
 
-H(alternative): There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.
+H\textsubscript{a}: There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.
 
@@
     axis.title.y = element_text(color = "black", size=12, vjust = 3),
-    axis.title.y.right = element_text(color = "black", size=12, vjust = 3)
+    axis.title.y.right = element_text(color = "black", size=12, vjust = 3),
+    text=element_text(family="CMU Serif")
   ) +
@@
   ggtitle("Development of Policy Stringency and Mobility Reduction in Europe")
-
 ```
@@
   ggtitle("Policy Compliance in Europe") +
-  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) 
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
+        text=element_text(family="CMU Serif"))
 ```
@@
     axis.title.y = element_text(color = "black", size=12, vjust = 3),
-    axis.title.x = element_text(size=12, vjust = 0.5)
+    axis.title.x = element_text(size=12, vjust = 0.5),
+    text=element_text(family="CMU Serif")
     ) +

### 2020-12-25 Script.R

@@ -8,11 +8,6 @@ library(plotly)
 library(reshape2)
 library(utils)
 
-# Hypothesis
-#H₀: There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.
-
-#Hₐ: There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.
-
 # Data Wrangling -----
 ## Adding the Policy Data -----
 ### Read in the Data
@@ -195,14 +190,11 @@ ggplot(data) +
 
 ## Non-hierarchical model ----
 
-`Compliance Index = β₀ + β₁ × Date + β₂ × Country + β₃ × Publicity + β₄ × Cases per 100.000 per 14 days + ε`
-
-
 lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days)
 
 summary(lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days))
 
-### Creating nice regression table output
+### Creating nice regression table output ----
 lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)
 
 #### Modify htmlreg arguments in order to improve table output
@@ -236,14 +228,9 @@ rstudioapi::viewer(htmlFile)
 
 ### Visualising different predicted intercepts and different slopes
 ggplot(data = augment(lm(data = data, 
-                         MobilityIndex ~ Date + CountryName + StringencyIndex)),
-       aes(x = Date, y = MobilityIndex, color = CountryName))  +
+                         ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days)),
+       aes(x = Date, y = ComplianceIndex, color = CountryName))  +
   geom_smooth(aes(y = .fitted), method = "lm", se = FALSE)
-
-ggplot(data = augment(lm(data = data, 
-                         MobilityIndex ~ Date + CountryName + StringencyIndex)))  +
-  geom_line(aes(x = Date, y = .fitted, color = CountryName))
-
 
 ### Visualization of the non-hierarchical model ----
 

### 2020-12-25 Draft.Rmd
Added analysis with the hierarchical model

@@
 This suggests creating a hierarchical model with a random intercept for country in order to improve model fit.
+We can also see that the slopes do not differ substantially, so that for the sake of simplicity we can use only a random intercept in our model.
+
+\begin{equation}
+{Compliance Index}_{ij} = {\beta}_0 + {\beta}_1 * {Date}_{ij} + {\beta}_2 * {Publicity}_{ij} + {\beta}_3 * {Cases/100,000/14 days}_{ij} + {Country}_j + {\epsilon}_{ij}
+\end{equation}
+
+```{r Regression Table 2, echo=FALSE, fig.align='center', results="asis"}
+
+# Fit the model
+lmer_out <- lmer(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days +  (1 | CountryName))
+
+# Generate regression table
+texreg::texreg(lmer_out, single.row = TRUE, 
+                         #                         custom.header = list("Model Results" = 1),
+                         #                         model.names = c("My name 1", "My name 2"), 
+                         custom.coef.names = c("Intercept", "Date", "Publicity",
+                                               "Cases/100,000/14 Days"),
+                                               #"Belgium",
+                                               #"Denmark",
+                                               #"France",
+                                               #"Germany",
+                                               #"Ireland",
+                                               #"Italy",
+                                               #"Netherlands",
+                                               #"Poland",
+                                               #"Spain",
+                                               #"Sweden",
+                                               #"United Kingdom"),
+                         bold = 0.05,
+                         center = TRUE,
+                         caption = "Regression Table 2"
+)
+
+```
+
+As we can see, the coefficients of the fixed effects at level one have not changed substantially, except for the fact that the predictor Cases/100,000/14Days has now become statistically significant.
+More interesting are the changes in the effects of our grouping variable.
 

### 2020-12-25 Script.R

@@ -182,7 +182,7 @@ ggplot(data) +
   scale_y_continuous(name = "Policy Compliance Index") +
   theme(
     axis.title.y = element_text(color = "black", size=12, vjust = 3),
-    axis.title.x = element_text(size=12, vjust = 0.5)
+    axis.title.x = element_text(size=12, vjust = 0.5),
     ) +
   ggtitle("Policy Compliance in Europe Across Time")
 

### 2020-12-26 Draft.Rmd
Improved text and changed appearance of plots

@@
 
-To find an answer to these questions, the following analysis will assess the following hypothesis.
+To find an answer to these questions, the following analysis will assess the following hypotheses.
 
-H\textsubscript{0}: There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.
+H\textsubscript{0}: There **is no** difference in compliance with mobility-reducing policies across European countries and this policy-compliance **does not** express a trend.
 
-H\textsubscript{a}: There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.
+H\textsubscript{a}: There **is** a difference in compliance with mobility-reducing policies across European countries and this policy-compliance **does** express a trend.
 
@@
 
+For this analysis, policy-compliance is approximated as the difference between the level of policy-stringency and the observed reduction in mobility.
+
+`Compliance = 100 - (Policy Stringency Index - %-change in Mobility)`
+
+To assess our hypothesis more thoroughly, policy-compliance is additionally corrected for COVID-19-cases [@Data14DayNotification2020] and public attention on the topic, as approximated by Google search queries with the terms *"covid"* & *"coronavirus"* [@GoogleTrends].
+
 Countries included in the analysis were chosen based on their membership to the EU (including the United Kingdom) and their GDP.
 
-The following diagram shows how in March, April and May lock style policies were introduced and how mobility was reduced in concordance in almost all of the countries assessed.
-However, beginning immediately from there on, mobility started to increase again, with the gap between policy stringency and observed mobility-reduction widening.
-Note that policy stringency is on the left y-axis and mobility changes on the right.
-The scale of policy stringency is reversed for better comparability.
+The following diagram shows how in March, April and May lockdown-style policies were introduced and how mobility was reduced in concordance in almost all of the countries assessed.
+However, beginning immediately from there on, mobility started to increase again, with the gap between policy stringency and observed mobility-reduction widening - signaling reduced levels of policy-compliance.
 
@@
     axis.title.y.right = element_text(color = "black", size=12, vjust = 3),
-    text=element_text(family="CMU Serif")
+    text=element_text(family="CMU Serif"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
+    strip.background = element_rect(fill="white")
   ) +
@@
 
-For this analysis, policy-compliance is approximated as the difference between the level of policy-stringency and the observed reduction in mobility.
-
-`Compliance = 100 - (Policy Stringency Index - %-change in Mobility)`
-
-The boxplot shows us that, indeed, the levels of policy compliance among European countries differ.
+The boxplot shows us that, indeed, the levels of policy compliance across European countries differ while the intra-group variance is roughly the same.
 
@@
   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
-        text=element_text(family="CMU Serif"))
+        text=element_text(family="CMU Serif"),
+        panel.background = element_rect(fill = "white"),
+        panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
 ```
@@
     axis.title.x = element_text(size=12, vjust = 0.5),
-    text=element_text(family="CMU Serif")
+    text=element_text(family="CMU Serif"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
+    strip.background = element_rect(fill="white")
   ) +

### 2020-12-26 Script.R

@@ -271,31 +271,48 @@ plot_ly(data = subset(data, CountryName == "Austria"), z = ~MobilityIndex, x = ~
 plot_ly(data, x = ~Date, y = ~StringencyIndex, z = ~MobilityIndex, color = ~CountryName, type = 'scatter3d', mode = 'lines',
                opacity = 0.6, line = list(width = 3, reverscale = FALSE))
 
-## How does the mobility change over time in Europe? - I do understand this model ----
-lmer_out <- lmer(data = data, MobilityIndex ~ StringencyIndex + Date + (Date | CountryName))
-
-### Looking at the results
-summary(lmer(data = data, MobilityIndex ~ StringencyIndex + Date + (Date | CountryName)))
-
-### extract out the fixed effect for date
-fixef(lmer(data = data, MobilityIndex ~ StringencyIndex + Date + (Date | CountryName)))
-
-### extract out the random effect for country
-ranef(lmer(data = data, MobilityIndex ~ StringencyIndex + Date + (Date | CountryName)))
-
 ## How does the Compliance change over time in Europe? This model has not enough independent variables ----
 
-lmer_out <- lmer(data = data, ComplianceIndex ~ Date + (Date | CountryName))
+lmer_out <- lmer(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days +  (1 | CountryName))
 
 ### Looking at the results
-summary(lmer(data = data, ComplianceIndex ~ Date + (Date | CountryName)))
+summary(lmer_out)
 
 ### extract out the fixed effect for date
-fixef(lmer(data = data, ComplianceIndex ~ Date + (Date | CountryName)))
+fixef(lmer_out)
 
 ### extract out the random effect for country
-ranef(lmer(data = data, ComplianceIndex ~ Date + (Date | CountryName)))
+ranef(lmer_out)
 
+### Formatting the regression table
+#### Modify htmlreg arguments in order to improve table output
+#### Then insert the texreg statement in Rmd
+table <- texreg::htmlreg(lmer_out, single.row = TRUE, 
+                        #                         custom.header = list("Model Results" = 1),
+                        #                         model.names = c("My name 1", "My name 2"), 
+                        custom.coef.names = c("Intercept", "Date", "Publicity",
+                                              "Cases/100,000/14 Days"),
+                        #"Belgium",
+                        #"Denmark",
+                        #"France",
+                        #"Germany",
+                        #"Ireland",
+                        #"Italy",
[…]

### 2020-12-26 Draft.Rmd
Replaced automatically created regression tables with manually created markdown table. Added PDF with embedded fonts.

@@
 Date is statistically significant at the 0.05 level.
-It's coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases by 0.07 points each day.
+It's coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases on average by 0.07 points each day.
+
+| Variable              | Coefficient | Std. Error | P-Value |
+| --------------------- | -----------: | ----------: | :-------: |
+| Date                  | −0.07       | 0.01     | ∗∗∗     |
+| Publicity             | −0.01       | 0.02     |         |
+| Cases/100,000/14 Days | 0.00        | 0.00     |         |
+| Belgium               | −3.21       | 2.12     |         |
+| Denmark               | -8.29       | 2.12       | ∗∗∗     |
+| France                | -7.15       | 2.11     | ∗∗∗     |
+| Germany               | −11.06      | 2.12     | ∗∗∗     |
+| Ireland               | −4.07       | 2.13     |         |
+| Italy                 | −8.12       | 2.17     | ∗∗∗     |
+| Netherlands           | −2.97       | 2.14     |         |
+| Poland                | −5.67       | 2.17     | ∗∗      |
+| Spain                 | −4.79       | 2.24     | ∗       |
+| Sweden                | −9.53       | 2.11     | ∗∗∗     |
+| United Kingdom        | −3.25       | 2.13     |         |
+R\textsuperscript{2} = 0.31;
+Adj. R\textsuperscript{2} = 0.29;
+Num. obs. = 520;
+∗∗∗ p < 0.001; ∗∗ p < 0.01; ∗ p < 0.05
 
@@
 
-```{r Regression Table, echo=FALSE, fig.align='center', results="asis"}
-
-# Fit the model
-lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)
-
-# Generate regression table
-texreg::texreg(lm1, single.row = TRUE, 
-#                         custom.header = list("Model Results" = 1),
-#                         model.names = c("My name 1", "My name 2"), 
-                         custom.coef.names = c("Intercept", "Date", "Publicity",
-                                               "Cases/100,000/14 Days",
-                                               "Belgium",
-                                               "Denmark",
-                                               "France",
-                                               "Germany",
-                                               "Ireland",
-                                               "Italy",
-                                               "Netherlands",
-                                               "Poland",
-                                               "Spain",
-                                               "Sweden",
-                                               "United Kingdom"),
-                          bold = 0.05,
-                          center = TRUE,
-                          caption = "Regression Table"
-                         )
-```
-
 ## Linear Multi-Level Model
 
-However, when plotting the fitted values from the non-hierarchical linear model by country, we can observe different discrete levels of compliance by date, e.g.
-with Austria showing much higher levels of compliance than Germany and Sweden.
+As we can see in the regression output of our non-hierarchical model, the fixed effects estimated for the different expressions of our country variable show substantial differences, with Germany showing more than 10 points less policy-compliance than our reference country Austria.
 
-```{r Linear model predictions by country, echo=FALSE, fig.align='center', message=FALSE, warning=FALSE}
-### Visualising different predicted intercepts and different slopes
+Additionally, the following plot shows slightly different slopes of the countries.
+
+```{r Non-hierarchical different intercepts and slopes, message=FALSE, warning=FALSE}
 ggplot(data = augment(lm(data = data, 
@@
     axis.title.x = element_text(size=12, vjust = 0.5),
-    text=element_text(family="CMU Serif")
+    text=element_text(family="CMU Serif"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_line(colour = "grey", linetype = "dotted")
   ) +
@@
 
-This suggests creating a hierarchical model with a random intercept for country in order to improve model fit.
-We can also see that the slopes do not differ substantially, so that for the sake of simplicity we can use only a random intercept in our model.
+Thus, in order to better assess the trends of policy-compliance in Europe over time, we can create a hierarchical model, allowing both random intercepts for the subgroups of Country as our grouping variable and random slopes along the Date variable.
 
 \begin{equation}
-{Compliance Index}_{ij} = {\beta}_0 + {\beta}_1 * {Date}_{ij} + {\beta}_2 * {Publicity}_{ij} + {\beta}_3 * {Cases/100,000/14 days}_{ij} + {Country}_j + {\epsilon}_{ij}
+{Compliance Index}_{ij} = {\beta}_0 + ({\beta}_1 * {Date}_{ij}) + {\beta}_2 * {Publicity}_{ij} + {\beta}_3 * {Cases/100,000/14 days}_{ij} + {Country}_{0j} + {\epsilon}_{0ij}
 \end{equation}
-
-```{r Regression Table 2, echo=FALSE, fig.align='center', results="asis"}
-
-# Fit the model
-lmer_out <- lmer(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days +  (1 | CountryName))
-
-# Generate regression table
-texreg::texreg(lmer_out, single.row = TRUE, 
-                         #                         custom.header = list("Model Results" = 1),
-                         #                         model.names = c("My name 1", "My name 2"), 
-                         custom.coef.names = c("Intercept", "Date", "Publicity",
-                                               "Cases/100,000/14 Days"),
-                                               #"Belgium",
-                                               #"Denmark",
-                                               #"France",
-                                               #"Germany",
-                                               #"Ireland",
-                                               #"Italy",
-                                               #"Netherlands",
-                                               #"Poland",
-                                               #"Spain",
-                                               #"Sweden",
-                                               #"United Kingdom"),
-                         bold = 0.05,
-                         center = TRUE,
-                         caption = "Regression Table 2"
-)
-
-```
 

### 2020-12-26 Draft.Rmd
Included further analysis for the hierarchical model and code chunks for the models.

@@
 library(stargazer)
+library(lmtest)
 library(extrafont)
@@
 
+```{r Non-Hiearchical Model, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+## Fit the model
+lm_out <- lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days)
+
+## Look at the results
+summary(lm_out)
+
+## Call:
+## lm(formula = ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days, 
+##     data = data)
+## 
+## Residuals:
+##     Min      1Q  Median      3Q     Max 
+## -39.271  -6.424  -0.826   6.354  42.727 
+## 
+## Coefficients:
+##                                                   Estimate Std. Error t value Pr(>|t|)    
+## (Intercept)                                      1.430e+03  1.181e+02  12.113   <2e-16 ***
+## Date                                            -7.442e-02  6.400e-03 -11.627   <2e-16 ***
+## Publicity                                       -8.653e-03  2.192e-02  -0.395    0.693    
+## notification_rate_per_100000_population_14.days  6.592e-03  2.551e-03   2.584    0.010 *  
+## ---
+## Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+## 
+## Residual standard error: 10.28 on 516 degrees of freedom
+##   (3797 observations deleted due to missingness)
+## Multiple R-squared:  0.2418,	Adjusted R-squared:  0.2374 
+## F-statistic: 54.86 on 3 and 516 DF,  p-value: < 2.2e-16
+
+```
+
 | Variable              | Coefficient | Std. Error | P-Value |
@@
 As we can see in the regression output of our non-hierarchical model, the fixed effects estimated for the different expressions of our country variable show substantial differences, with Germany showing more than 10 points less policy-compliance than our reference country Austria.
-
-Additionally, the following plot shows slightly different slopes of the countries.
+Additionally, the following plot shows that the slopes for Compliance vs.
+Date by Country differ slightly.
 
@@
 \begin{equation}
-{Compliance Index}_{ij} = {\beta}_0 + ({\beta}_1 * {Date}_{ij}) + {\beta}_2 * {Publicity}_{ij} + {\beta}_3 * {Cases/100,000/14 days}_{ij} + {Country}_{0j} + {\epsilon}_{0ij}
+{Compliance Index}_{ij} = {\beta}_0 + {\beta}_1 * {Date}_{ij} + {\beta}_2 * {Publicity}_{ij} + {\beta}_3 * {Cases/100,000/14 days}_{ij} + {\beta}_{1j} * {Date} + {Country}_{0j} + {\epsilon}_{0ij}
 \end{equation}
 
-As we can see, the coefficients of the fixed effects at level one have not changed substantially, except for the fact that the predictor Cases/100,000/14Days has now become statistically significant.
-More interesting are the changes in the effects of our grouping variable.
+```{r Hierarchical model, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+## How does the Compliance change over time in Europe? This model has not enough independent variables ----
+
+lmer_out <- lmer(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days +  (Date | CountryName))
+
+### Looking at the results
+summary(lmer_out3)
+
+## Linear mixed model fit by REML ['lmerMod']
+## Formula: ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days +  
+##     (Date | CountryName)
+##    Data: data
+## 
+## REML criterion at convergence: 3908.6
+## 
+## Scaled residuals: 
+##     Min      1Q  Median      3Q     Max 
+## -3.7395 -0.6504 -0.0370  0.5971  3.7889 
+## 
+## Random effects:
+##  Groups      Name        Variance  Std.Dev.  Corr 
+##  CountryName (Intercept) 9.644e+01 9.8205986      
+##              Date        9.074e-07 0.0009526 -1.00
+##  Residual                9.643e+01 9.8196921      
+## Number of obs: 520, groups:  CountryName, 12
+## 
+## Fixed effects:
+##                                                   Estimate Std. Error t value
+## (Intercept)                                      1.376e+03  1.145e+02  12.015
+## Date                                            -7.148e-02  6.213e-03 -11.505
+## Publicity                                       -1.027e-02  2.362e-02  -0.435
+## notification_rate_per_100000_population_14.days  4.744e-03  2.533e-03   1.873
+## 
+## Correlation of Fixed Effects:
+##             (Intr) Date   Pblcty
+## Date        -1.000              
+## Publicity   -0.155  0.148       
+## n___100000_  0.610 -0.610 -0.288
+## optimizer (nloptwrap) convergence code: 0 (OK)
+## boundary (singular) fit: see ?isSingular
+
+### Getting p-values
+
+2*pt(11.505, 520, lower.tail = F)
+
+2*pt(0.435, 520, lower.tail = F)
+
+2*pt(1.873, 520, lower.tail = F)
+
+## > 2*pt(11.505, 520, lower.tail = F)
+## [1] 1.906225e-27
+## > 2*pt(0.435, 520, lower.tail = F)
+## [1] 0.6637429
+## > 2*pt(1.873, 520, lower.tail = F)
+## [1] 0.06162918
+
+```
+
+| Random effects | -         | -        | -         |
+| -------------- | --------- | --------: | ---------: |
+| Groups         | Name      | Variance | Std. Dev. |
+| Country        | Intercept | 96.44 | 9.82      |
+|                | Date      | 0.00 | 0.00      |
+| Residual       |  |   96.43 |    9.82         |
+Number of observations: 520, Number of groups: 12
+
+| Fixed effects         | -         | -          | -       |   -  |
+| --------------------- | ---------: | ----------: | -------: | :---: |
+|                       | Estimate  | Std. Error | t-value |   p-value  |
+| Date                  | -0.07 | 0.01  | -11.51  | ∗∗∗   |
+| Publicity             | -0.01 | 0.02   | -0.44   |     |
+| Cases/100,000/14 Days | 0.00  | 0.00   | 1.87    |    |
+∗∗∗ p < 0.001; ∗∗ p < 0.01; ∗ p < 0.05
+
+As we can see, the coefficients of the fixed effects at level one have not changed substantially.
+Still, the fixed effect of Date is the only one that is statistically significant.
+The fact that the variance of the residual is almost as big as the variance of the random intercepts casts in doubt the explanatory value of our model.
+
+## Model comparison
+
+```{r Likelihood ratio test, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+
+lrtest(lm_out, lmer_out)
+
+## Likelihood ratio test
+## 
+## Model 1: ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days
+## Model 2: ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + 
+##     (Date | CountryName)
+##   #Df  LogLik Df  Chisq Pr(>Chisq)   
+## 1   5 -1947.3                        
+## 2   8 -1954.3  3 13.991   0.002917 **
+## ---
+## Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+```
 

### 2020-12-26 Script.R

@@ -7,6 +7,11 @@ library(broom.mixed)
 library(plotly)
 library(reshape2)
 library(utils)
+library(texreg)
+library(stargazer)
+library(extrafont)
+library(lmtest)
+loadfonts()
 
 # Data Wrangling -----
 ## Adding the Policy Data -----
@@ -141,13 +146,20 @@ data$ComplianceIndex <- rescale(data$ComplianceIndex, to = c(0, 100))
 
 # Explorative Data Visualization ----
 
+
+## Correlation table
+pairs(subset(data, select = c(Date, Publicity, ComplianceIndex, notification_rate_per_100000_population_14.days)))
+
 ## Create a Boxplot of Compliance by Country ----
 ggplot(data = data, aes(x = CountryName, y = ComplianceIndex)) +
   geom_boxplot() +
   xlab("Country") +
   ylab("Policy Compliance Index") +
   ggtitle("Policy Compliance in Europe") +
-  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) 
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
+        text=element_text(family="CMU Serif"),
+        panel.background = element_rect(fill = "white"),
+        panel.grid.major = element_line(colour = "grey", linetype = "solid"))
 
 ## Create a faceted plot with Stringency and Mobility for European Countries ----
 
@@ -164,7 +176,11 @@ ggplot(data = data) +
   theme(
     axis.title.x = element_text(vjust = 0.5),
     axis.title.y = element_text(color = "black", size=12, vjust = 3),
-    axis.title.y.right = element_text(color = "black", size=12, vjust = 3)
+    axis.title.y.right = element_text(color = "black", size=12, vjust = 3),
+    text=element_text(family="CMU Serif"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
+    strip.background = element_rect(fill="white")
   ) +
   geom_hline(yintercept = 0, color = "black", size = 0.5) +
   ggtitle("Development of Policy Stringency and Mobility Reduction in Europe")
@@ -183,16 +199,20 @@ ggplot(data) +
   theme(
     axis.title.y = element_text(color = "black", size=12, vjust = 3),
     axis.title.x = element_text(size=12, vjust = 0.5),
-    ) +
[…]

### 2020-12-26 Script.R
Finalized formatting

@@ -177,10 +177,11 @@ ggplot(data = data) +
     axis.title.x = element_text(vjust = 0.5),
     axis.title.y = element_text(color = "black", size=12, vjust = 3),
     axis.title.y.right = element_text(color = "black", size=12, vjust = 3),
-    text=element_text(family="CMU Serif"),
+    text=element_text(family="CMU Sans Serif"),
     panel.background = element_rect(fill = "white"),
     panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
-    strip.background = element_rect(fill="white")
+    strip.background = element_rect(fill="white"),
+    plot.title = element_text(size = 11, face = "bold")
   ) +
   geom_hline(yintercept = 0, color = "black", size = 0.5) +
   ggtitle("Development of Policy Stringency and Mobility Reduction in Europe")

### 2020-12-26 Draft.Rmd

@@
 author: "Philipp Holz"
-date: 'December 24, 2020'
+#date: "`r format(Sys.time(), '%d %B, %Y')`"
+date: "26 December 2020"
 output: 
@@
     latex_engine: xelatex
+    fig_width: 6
+    fig_height: 4
 bibliography: References.json
@@
 
-The COVID-19-Pandemic is an ongoing challenge for policy-makers.
+The COVID-19-Pandemic is an ongoing challenge for policymakers.
 Especially, because overcoming it is so dependent on the policy-compliance of each and every individual.
@@
 
-This analysis combines data from the Google COVID-19 Community Mobility Reports [@COVID19CommunityMobility2020] and data from the the Oxford Policy Tracker [@haleOxfordCOVID19Government2020].
+This analysis combines data from the Google COVID-19 Community Mobility Reports [@COVID19CommunityMobility2020] and data from the Oxford Policy Tracker [@haleOxfordCOVID19Government2020].
 The Google Mobility Report charts "movement trends over time by geography, across different categories."[@COVID19CommunityMobility2020] For the sake of this analysis the movement trends of the categories retail and recreation, supermarkets and pharmacies, public transport and workplaces were included and averaged without weighting.
@@
 
-The following diagram shows how in March, April and May lockdown-style policies were introduced and how mobility was reduced in concordance in almost all of the countries assessed.
+The following diagram shows how in March, April and May lockdown-style policies were introduced and how mobility was reduced in concordance in almost all the countries assessed.
 However, beginning immediately from there on, mobility started to increase again, with the gap between policy stringency and observed mobility-reduction widening - signaling reduced levels of policy-compliance.
@@
     axis.title.y.right = element_text(color = "black", size=12, vjust = 3),
-    text=element_text(family="CMU Serif"),
+    text=element_text(family="CMU Sans Serif"),
     panel.background = element_rect(fill = "white"),
     panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
-    strip.background = element_rect(fill="white")
+    strip.background = element_rect(fill="white"),
+    plot.title = element_text(size = 11, face = "bold")
   ) +
@@
   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
-        text=element_text(family="CMU Serif"),
+        text=element_text(family="CMU Sans Serif"),
         panel.background = element_rect(fill = "white"),
-        panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
+        panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
+        plot.title = element_text(size = 11, face = "bold"))
 ```
@@
   geom_smooth(aes(x = Date, y = ComplianceIndex), method = "loess", se = FALSE, span = 1/10, 
-              color = "black", linetype = "solid", size = 0.1) +
+              color = "black", linetype = "solid", size = 0.2) +
   geom_smooth(aes(x = Date, y = ComplianceIndex), method = "lm", se = FALSE, 
@@
     axis.title.x = element_text(size=12, vjust = 0.5),
-    text=element_text(family="CMU Serif"),
+    text=element_text(family="CMU Sans Serif"),
     panel.background = element_rect(fill = "white"),
     panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
-    strip.background = element_rect(fill="white")
-  ) +
+    strip.background = element_rect(fill="white"),
+    plot.title = element_text(size = 11, face = "bold")) +
   ggtitle("Policy Compliance in Europe Across Time")
@@
 It yields the following result.
-Except for Date, non of the continuous variables Publicity and Cases/100.000/14 Days are statistically significant.
+Except for Date, none of the continuous variables Publicity and Cases/100.000/14 Days are statistically significant.
 Date is statistically significant at the 0.05 level.
-It's coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases on average by 0.07 points each day.
+Its coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases on average by 0.07 points each day.
 
@@
 
-With Country as the categorical variable, all expressions are statistically significant at the 0.05 level, with the exception of Belgium, Ireland, the Netherlands and the United Kingdom, when compared to Austria as the reference category.
+With Country as the categorical variable, all expressions are statistically significant at the 0.05 level, with the exception of Belgium, Ireland, the Netherlands, and the United Kingdom, when compared to Austria as the reference category.
 The adjusted R² indicates that the model explains 29% of the observed variance.
@@
 
-```{r Non-hierarchical different intercepts and slopes, message=FALSE, warning=FALSE}
+```{r Non-hierarchical different intercepts and slopes, message=FALSE, warning=FALSE, fig.align = "center"}
 ggplot(data = augment(lm(data = data, 
@@
     axis.title.x = element_text(size=12, vjust = 0.5),
-    text=element_text(family="CMU Serif"),
+    text=element_text(family="CMU Sans Serif"),
     panel.background = element_rect(fill = "white"),
-    panel.grid.major = element_line(colour = "grey", linetype = "dotted")
-  ) +
+    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
+    plot.title = element_text(size = 11, face = "bold")) +
   ggtitle("Model Predictions for Policy Compliance in Europe Across Time")
@@
 
-Thus, in order to better assess the trends of policy-compliance in Europe over time, we can create a hierarchical model, allowing both random intercepts for the subgroups of Country as our grouping variable and random slopes along the Date variable.
+Thus, to better assess the trends of policy-compliance in Europe over time, we can create a hierarchical model, allowing both random intercepts for the subgroups of Country as our grouping variable and random slopes along the Date variable.
 
@@
 | Random effects | -         |        - |         - |
-| -------------- | --------- | --------: | ---------: |
+| -------------- | --------- | --------:| ---------:|
 | Groups         | Name      | Variance | Std. Dev. |
@@
 | Fixed effects         |        - |          - |       - |    -    |
-| --------------------- | ---------: | ----------: | -------: | :---: |
+| --------------------- | --------:| ----------:| -------:|:-------:|
 |                       | Estimate | Std. Error | t-value | p-value |
@@
 
+Finally, to compare our hierarchical model-fit with the model-fit of our non-hierarchical model, we can compute a likelihood ratio test. This yields the following result.
+
+`Model 1: ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days`
+
+`Model 2: ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + (Date | CountryName)`
+
+| Model | Df  | LogLik  | Chisq  | Pr(>Chisq)  |
+| ----- | --- | ------- | ------ | ----------- |
+| 1     | 5   | -1947.3 |        |             |
+| 2     | 8   | -1954.3 | 13.991 | 0.002917 ** |
+∗∗∗ p < 0.001; ∗∗ p < 0.01; ∗ p < 0.05
+
+As we can see, the improvement of our hierarchical model over our non-hierarchical model is statistically significant at the 0.05 level.
+
+# Conclusion
+
+This analysis has shown that, interestingly, levels of compliance with mobility-reducing COVID-19-policies differ across selected European countries and that policy-compliance expresses an alarming, negative trend.
+We were able to show these findings using both a non-hierarchical and a hierarchical model.
+Nevertheless, this analysis has also shown that a large amount of variance in policy compliance remains unexplained by our models, which might be due to their linear character.
+Further attempts will have to be made in that regard.
+
 # References

### 2020-12-26 Draft.Rmd
changed & to and

@@
 
-To assess our hypothesis more thoroughly, policy-compliance is additionally corrected for COVID-19-cases [@Data14DayNotification2020] and public attention on the topic, as approximated by Google search queries with the terms *"covid"* & *"coronavirus"* [@GoogleTrends].
+To assess our hypothesis more thoroughly, policy-compliance is additionally corrected for COVID-19-cases [@Data14DayNotification2020] and public attention on the topic, as approximated by Google search queries with the terms *"covid"* and *"corona"* [@GoogleTrends].
 

### 2021-01-04 Script.R
reworked analysis and added plot on rate of change of policy in europe

@@ -145,8 +145,6 @@ data$ComplianceIndex <- rescale(data$ComplianceIndex, to = c(0, 100))
 
 
 # Explorative Data Visualization ----
-
-
 ## Correlation table
 pairs(subset(data, select = c(Date, Publicity, ComplianceIndex, notification_rate_per_100000_population_14.days)))
 
@@ -208,10 +206,15 @@ ggplot(data) +
   ggtitle("Policy Compliance in Europe Across Time")
 
 # Modelling ----
+## Non-hierarchical model 1 ----
 
-## Non-hierarchical model ----
+lm_out <- lm(data = data, ComplianceIndex ~ Date + CountryName)
 
-lm_out <- lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days)
+summary(lm_out)
+
+## Non-hierarchical model 2 ----
+
+lm_out <- lm(data = data, ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days)
 
 summary(lm_out)
 
@@ -312,7 +315,7 @@ plot_ly(data, x = ~Date, y = ~StringencyIndex, z = ~MobilityIndex, color = ~Coun
 
 ## How does the Compliance change over time in Europe? This model has not enough independent variables ----
 
-lmer_out <- lmer(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days +  (Date | CountryName))
+lmer_out <- lmer(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + (Date | CountryName))
 
 ### Looking at the results
 summary(lmer_out)
@@ -365,18 +368,6 @@ rstudioapi::viewer(table)
 
 lrtest(lm_out, lmer_out)
 
-## Warning in modelUpdate(objects[[i - 1]], objects[[i]]): original model was of
-## class "lmerMod", updated model is of class "lm"
-## Likelihood ratio test
-## 
-## Model 1: LabVote19 ~ LabVote17 + Leave16Vote + (1 | region)
-## Model 2: LabVote19 ~ LabVote17 + Leave16Vote + region - 1
-##   #Df  LogLik Df  Chisq Pr(>Chisq)    
-## 1   5 -1738.8                         
-## 2  14 -1713.8  9 50.053  1.053e-07 ***
-## ---
[…]

### 2021-01-04 Draft.Rmd

@@
 #date: "`r format(Sys.time(), '%d %B, %Y')`"
-date: "26 December 2020"
+date: "05 January 2021"
 output: 
@@
 
-H\textsubscript{0}: There **is no** difference in compliance with mobility-reducing policies across European countries and this policy-compliance **does not** express a trend.
+H1\textsubscript{0}: There **is no** difference in compliance with mobility-reducing policies across European countries.
 
-H\textsubscript{a}: There **is** a difference in compliance with mobility-reducing policies across European countries and this policy-compliance **does** express a trend.
+H1\textsubscript{a}: There **is** a difference in compliance with mobility-reducing policies across European countries.
+
+H2\textsubscript{0}: There **is no** linear trend in such compliance over time.
+
+H2\textsubscript{a}: There **is** a linear trend in such compliance over time.
 
@@
 
-The following non-hierarchical model predicts the Mobility Index as the dependent variable, with the Stringency Index, Date and Country as the independent variables.
+The following non-hierarchical model predicts compliance as the dependent variable, with the Stringency Index, Date and Country as the independent variables.
 
 \begin{equation}
-{Compliance Index} = {\beta}_0 + {\beta}_1 * {Date} + {\beta}_2 * {Country} + {\beta}_3 * {Publicity} + {\beta}_4 * {Cases/100.000/14 days} + {\epsilon}
+{Compliance} = {\beta}_0 + {\beta}_1 * {Date} + {\beta}_2 * {Country} + {\epsilon}
 \end{equation}
 
-It yields the following result.
-Except for Date, none of the continuous variables Publicity and Cases/100.000/14 Days are statistically significant.
-Date is statistically significant at the 0.05 level.
-Its coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases on average by 0.07 points each day.
-
-```{r Non-Hiearchical Model, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+```{r Non-Hiearchical Model 1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
 ## Fit the model
-lm_out <- lm(data = data, ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days)
+lm_out <- lm(data = data, ComplianceIndex ~ Date + CountryName)
 
@@
 ## Call:
-## lm(formula = ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days, 
-##     data = data)
+## lm(formula = ComplianceIndex ~ Date + CountryName, data = ## data)
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-## -39.271  -6.424  -0.826   6.354  42.727 
+## -52.809  -6.508  -0.297   6.226  40.292 
+## 
+## Coefficients:
+##                             Estimate Std. Error t value ## Pr(>|t|)    
+## (Intercept)                1.223e+03  3.575e+01  34.211  < ## 2e-16 ***
+## Date                      -6.291e-02  1.936e-03 -32.489  < ## 2e-16 ***
+## CountryNameBelgium        -3.599e+00  8.334e-01  -4.318 ## 1.61e-05 ***
+## CountryNameDenmark        -9.119e+00  8.314e-01 -10.969  < ## 2e-16 ***
+## CountryNameFrance         -7.065e+00  8.314e-01  -8.497  < ## 2e-16 ***
+## CountryNameGermany        -1.196e+01  8.314e-01 -14.385  < ## 2e-16 ***
+## CountryNameIreland        -5.587e+00  8.341e-01  -6.698 ## 2.43e-11 ***
+## CountryNameItaly          -7.642e+00  8.348e-01  -9.154  < ## 2e-16 ***
+## CountryNameNetherlands    -5.099e+00  8.444e-01  -6.039 ## 1.70e-09 ***
+## CountryNamePoland         -6.166e+00  8.327e-01  -7.404 ## 1.63e-13 ***
+## CountryNameSpain          -4.647e+00  8.348e-01  -5.566 ## 2.79e-08 ***
+## CountryNameSweden         -1.021e+01  8.314e-01 -12.279  < ## 2e-16 ***
+## CountryNameUnited Kingdom -2.807e+00  8.314e-01  -3.376 ## 0.000742 ***
+## ---
+## Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+## 
+## Residual standard error: 10.32 on 3646 degrees of freedom
+##   (670 observations deleted due to missingness)
+## Multiple R-squared:  0.2791,	Adjusted R-squared:  0.2768 
+## F-statistic: 117.7 on 12 and 3646 DF,  p-value: < 2.2e-16
+```
+
+It yields the following result.
+
+| Variable                  | Coefficient | Std. Error | P-Value |
+| ------------------------- | ----------- | ---------- | ------- |
+| Date                      | -6.291e-02  | 1.936e-03  | \*\*\*  |
+| Belgium                   | -3.599e+00  | 8.334e-01  | \*\*\*  |
+| Denmark                   | -9.119e+00  | 8.314e-01  | \*\*\*  |
+| France                    | -7.065e+00  | 8.314e-01  | \*\*\*  |
+| Germany                   | -1.196e+01  | 8.314e-01  | \*\*\*  |
+| Ireland                   | -5.587e+00  | 8.341e-01  | \*\*\*  |
+| Italy                     | -7.642e+00  | 8.348e-01  | \*\*\*  |
+| Netherlands               | -5.099e+00  | 8.444e-01  | \*\*\*  |
+| Poland                    | -6.166e+00  | 8.327e-01  | \*\*\*  |
+| Spain                     | -4.647e+00  | 8.348e-01  | \*\*\*  |
+| Sweden                    | -1.021e+01  | 8.314e-01  | \*\*\*  |
+| United Kingdom            | -2.807e+00  | 8.314e-01  | \*\*\*  |
+R\textsuperscript{2} = 0.28;
+Adj. R\textsuperscript{2} = 0.28;
+Num. obs. = 520;
+∗∗∗ p < 0.001; ∗∗ p < 0.01; ∗ p < 0.0
+
+The coefficients for Data and the individual Countries, when compared to Austria, are statistically significant.
+The coefficient for date is negative, with only little standard error.
+Also the coefficients for the countries are negative, signalling that Austria showed the highest level of compliance, with Germany and Sweden at the bottom of the list.
+We can control this relationship for the influence of public attention to the pandemic and for COVID-19 cases per 100.000 and 14 days.
+
+\begin{equation}
+{Compliance} = {\beta}_0 + {\beta}_1 * {Date} + {\beta}_2 * {Country} + {\beta}_3 * {Public Attention} + {\beta}_4 * {Cases/(100.000 * 14 days)} + {\epsilon}
+\end{equation}
+
+```{r Non-Hiearchical Model 2, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+## Fit the model
+lm_out <- lm(data = data, ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days)
+
+## Look at the results
+summary(lm_out)
+
+## Call:
+## lm(formula = ComplianceIndex ~ Date + CountryName + Publicity + 
+##     notification_rate_per_100000_population_14.days, data = data)
+## 
+## Residuals:
+##     Min      1Q  Median      3Q     Max 
+## -36.552  -6.433  -0.435   5.822  37.089 
 ## 
@@
 ##                                                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)                                      1.430e+03  1.181e+02  12.113   <2e-16 ***
-## Date                                            -7.442e-02  6.400e-03 -11.627   <2e-16 ***
-## Publicity                                       -8.653e-03  2.192e-02  -0.395    0.693    
-## notification_rate_per_100000_population_14.days  6.592e-03  2.551e-03   2.584    0.010 *  
+## (Intercept)                                      1.381e+03  1.155e+02  11.953  < 2e-16 ***
+## Date                                            -7.142e-02  6.264e-03 -11.401  < 2e-16 ***
+## CountryNameBelgium                              -3.211e+00  2.122e+00  -1.514 0.130771    
+## CountryNameDenmark                              -8.285e+00  2.124e+00  -3.902 0.000108 ***
+## CountryNameFrance                               -7.145e+00  2.112e+00  -3.383 0.000773 ***
+## CountryNameGermany                              -1.106e+01  2.124e+00  -5.209 2.77e-07 ***
+## CountryNameIreland                              -4.066e+00  2.133e+00  -1.906 0.057210 .  
+## CountryNameItaly                                -8.116e+00  2.165e+00  -3.748 0.000199 ***
+## CountryNameNetherlands                          -2.967e+00  2.142e+00  -1.385 0.166606    
+## CountryNamePoland                               -5.667e+00  2.169e+00  -2.613 0.009253 ** 
+## CountryNameSpain                                -4.790e+00  2.239e+00  -2.139 0.032904 *  
+## CountryNameSweden                               -9.533e+00  2.113e+00  -4.511 8.03e-06 ***
+## CountryNameUnited Kingdom                       -3.250e+00  2.126e+00  -1.529 0.126923    
+## Publicity                                       -1.085e-02  2.393e-02  -0.453 0.650518    
+## notification_rate_per_100000_population_14.days  4.710e-03  2.557e-03   1.842 0.066033 .  
 ## ---
@@
 ## 
-## Residual standard error: 10.28 on 516 degrees of freedom
-##   (3797 observations deleted due to missingness)
-## Multiple R-squared:  0.2418,	Adjusted R-squared:  0.2374 
-## F-statistic: 54.86 on 3 and 516 DF,  p-value: < 2.2e-16
+## Residual standard error: 9.907 on 505 degrees of freedom
+##   (3809 observations deleted due to missingness)
+## Multiple R-squared:  0.3102,	Adjusted R-squared:  0.2911 
+## F-statistic: 16.22 on 14 and 505 DF,  p-value: < 2.2e-16
 
@@
 
+It yields the following result.
+Except for Date, none of the continuous variables Public Attention and Cases per 100,000 and 14 Days are statistically significant.
+Date is statistically significant at the 0.05 level.
+Its coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases on average by 0.07 points each day.
+Interestingly, some of the coefficients for individual countries are not significant anymore when controlling for public attention and COVID-19 cases.
+In the following, a random intercept will be included for country, in order to improve model fit.
+
  | Variable                      | Coefficient | Std. Error | P-Value |
-| --------------------- | -----------: | ----------: | :-------: |
-| Date                  | −0.07       | 0.01     | ∗∗∗     |
-| Publicity             | −0.01       | 0.02     |         |
-| Cases/100,000/14 Days | 0.00        | 0.00     |         |
-| Belgium               | −3.21       | 2.12     |         |
-| Denmark               | -8.29       | 2.12       | ∗∗∗     |
-| France                | -7.15       | 2.11     | ∗∗∗     |
-| Germany               | −11.06      | 2.12     | ∗∗∗     |
-| Ireland               | −4.07       | 2.13     |         |
-| Italy                 | −8.12       | 2.17     | ∗∗∗     |
-| Netherlands           | −2.97       | 2.14     |         |
-| Poland                | −5.67       | 2.17     | ∗∗      |
-| Spain                 | −4.79       | 2.24     | ∗       |
-| Sweden                | −9.53       | 2.11     | ∗∗∗     |
-| United Kingdom        | −3.25       | 2.13     |         |
+ | ----------------------------- | ----------- | ---------- | ------- |
+ | Date                          | -7.142e-02  | 6.264e-03  | \*\*\*  |
+ | Belgium                       | -3.211e+00  | 2.122e+00  |         |
+ | Denmark                       | -8.285e+00  | 2.124e+00  | \*\*\*  |
+ | France                        | -7.145e+00  | 2.112e+00  | \*\*\*  |
+ | Germany                       | -1.106e+01  | 2.124e+00  | \*\*\*  |
+ | Ireland                       | -4.066e+00  | 2.133e+00  | .       |
+ | Italy                         | -8.116e+00  | 2.165e+00  | \*\*\*  |
+ | Netherlands                   | -2.967e+00  | 2.142e+00  |         |
+ | Poland                        | -5.667e+00  | 2.169e+00  | \*\*    |
+ | Spain                         | -4.790e+00  | 2.239e+00  | \*      |
+ | Sweden                        | -9.533e+00  | 2.113e+00  | \*\*\*  |
+ | United Kingdom                | -3.250e+00  | 2.126e+00  |         |
+ | Public Attention              | -1.085e-02  | 2.393e-02  |         |
+ | Cases per 100,000 and 14 Days | 4.710e-03   | 2.557e-03  | .       |
 R\textsuperscript{2} = 0.31;
@@
 
-With Country as the categorical variable, all expressions are statistically significant at the 0.05 level, with the exception of Belgium, Ireland, the Netherlands, and the United Kingdom, when compared to Austria as the reference category.
-The adjusted R² indicates that the model explains 29% of the observed variance.
-
 ## Linear Multi-Level Model
@@
 As we can see in the regression output of our non-hierarchical model, the fixed effects estimated for the different expressions of our country variable show substantial differences, with Germany showing more than 10 points less policy-compliance than our reference country Austria.
-Additionally, the following plot shows that the slopes for Compliance vs.
-Date by Country differ slightly.
 
-```{r Non-hierarchical different intercepts and slopes, message=FALSE, warning=FALSE, fig.align = "center"}
-ggplot(data = augment(lm(data = data, 
-                         ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days)),
-       aes(x = Date, y = ComplianceIndex, color = CountryName))  +
-  geom_smooth(aes(y = .fitted), method = "lm", se = FALSE) +
-  xlab("Month") +
-  scale_x_date(breaks = date_breaks("3 months"),
-               labels = date_format("%b\n%Y")) +
-  scale_y_continuous(name = "Policy Compliance Index") +
-  theme(
-    axis.title.y = element_text(color = "black", size=12, vjust = 3),
-    axis.title.x = element_text(size=12, vjust = 0.5),
-    text=element_text(family="CMU Sans Serif"),
-    panel.background = element_rect(fill = "white"),
-    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
-    plot.title = element_text(size = 11, face = "bold")) +
-  ggtitle("Model Predictions for Policy Compliance in Europe Across Time")
-```
-
-Thus, to better assess the trends of policy-compliance in Europe over time, we can create a hierarchical model, allowing both random intercepts for the subgroups of Country as our grouping variable and random slopes along the Date variable.
+To better assess the trends of policy-compliance in Europe over time, we can create a hierarchical model, allowing both random intercepts for the subgroups of Country as our grouping variable and random slopes along the Date variable.
 
 \begin{equation}
-{Compliance Index}_{ij} = {\beta}_0 + {\beta}_1 * {Date}_{ij} + {\beta}_2 * {Publicity}_{ij} + {\beta}_3 * {Cases/100,000/14 days}_{ij} + {\beta}_{1j} * {Date} + {Country}_{0j} + {\epsilon}_{0ij}
+{Compliance}_{ij} = {\beta}_0 + {\beta}_1 * {Date}_{ij} + {\beta}_2 * {Public Attention}_{ij} + {\beta}_3 * {Cases/(100,000 * 14 days)}_{ij} + {\beta}_{1j} * {Date} + {Country}_{0j} + {\epsilon}_{0ij}
 \end{equation}
@@
 ### Looking at the results
-summary(lmer_out3)
+summary(lmer_out)
 
@@
 | Fixed effects                 |        - |          - |       - |    -    |
-| --------------------- | --------:| ----------:| -------:|:-------:|
+| ------------------------------| --------:| ----------:| -------:|:-------:|
 |                               | Estimate | Std. Error | t-value | p-value |
 | Date                          |    -0.07 |       0.01 |  -11.51 |   ∗∗∗   |
-| Publicity             |    -0.01 |       0.02 |   -0.44 |         |
-| Cases/100,000/14 Days |     0.00 |       0.00 |    1.87 |         |
+| Public Attention              |    -0.01 |       0.02 |   -0.44 |         |
+| Cases per 100,000 and 14 Days |     0.00 |       0.00 |    1.87 |         |
 ∗∗∗ p < 0.001; ∗∗ p < 0.01; ∗ p < 0.05
 
-As we can see, the coefficients of the fixed effects at level one have not changed substantially.
-Still, the fixed effect of Date is the only one that is statistically significant.
-The fact that the variance of the residual is almost as big as the variance of the random intercepts casts in doubt the explanatory value of our model.
+As we can see, the coefficients of the fixed effects at level one have not changed substantially. Still, the fixed effect of Date is the only one that is statistically significant.
+
+The following plot shows the rate at which compliance changes per day in different European countries, according to our hierarchical model, that controls for public attention and COVID-19-cases.
+
+```{r slope of compliance-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center"}
+
+# Model
+lmer_out <- lmer(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days +  (Date | CountryName))
+
+## Extracting out the fixed-effect slope for Date
+Date_slope <- fixef(lmer_out)['Date']
+
+## Extracting out the random-effect slopes for Country
+Country_slope <- ranef(lmer_out)$CountryName
+
+## Creating a new column for the slope
+Country_slope$slope <- Country_slope$Date + Date_slope
+
+## Using row names to create a county name column
+Country_slope$country <- rownames(Country_slope)
+
+## Ordered county-level factor based upon slope values
+Country_slope$country_plot <- factor(Country_slope$country, 
+                                   levels = Country_slope$country[order(Country_slope$slope)])
+
+## Plotting the results
+ggplot(data = Country_slope, aes(x = country_plot, y = slope)) + 
+  geom_point() +
+  coord_flip() + 
+  theme_bw() + 
+  ylab("Change in Compliance per Day")  +
+  xlab("Country") +
+  theme(
+    axis.title.y = element_text(color = "black", size=12, vjust = 3),
+    axis.title.x = element_text(size=12, vjust = 0.5),
+    text=element_text(family="CMU Sans Serif"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
+    plot.title = element_text(size = 11, face = "bold")) +
+  ggtitle("Rate of Change in Compliance in Europe")
+```
 
@@
 ## 
-## Model 1: ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days
+## Model 1: ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days
 ## Model 2: ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + 
@@
 ##   #Df  LogLik Df Chisq Pr(>Chisq)    
-## 1   5 -1947.3                        
-## 2   8 -1954.3  3 13.991   0.002917 **
+## 1  16 -1922.8                        
+## 2   8 -1954.3 -8 63.15  1.119e-10 ***
 ## ---
@@
 
-`Model 1: ComplianceIndex ~ Date + Publicity + Date + notification_rate_per_100000_population_14.days`
+`Model 1: ComplianceIndex ~ Date + Country + Public Attention + Cases per 100,000 and 14 Days`
 
-`Model 2: ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + (Date | CountryName)`
+`Model 2: ComplianceIndex ~ Date + Public Attention + Cases per 100,000 and 14 Days + (Date | Country)`
 
-| Model | Df  | LogLik  | Chisq  | Pr(>Chisq)  |
-| ----- | --- | ------- | ------ | ----------- |
-| 1     | 5   | -1947.3 |        |             |
-| 2     | 8   | -1954.3 | 13.991 | 0.002917 ** |
+| Model | Df  | LogLik  | Chisq  | P-Value       |
+| ----- | --- | ------- | ------ | --------------|
+| 1     | 16  | -1922.8 |        |               |
+| 2     | 8   | -1954.3 | 63.15  | 1.119e-10 *** |
 ∗∗∗ p < 0.001; ∗∗ p < 0.01; ∗ p < 0.05
@@
 This analysis has shown that, interestingly, levels of compliance with mobility-reducing COVID-19-policies differ across selected European countries and that policy-compliance expresses an alarming, negative trend.
-We were able to show these findings using both a non-hierarchical and a hierarchical model.
-Nevertheless, this analysis has also shown that a large amount of variance in policy compliance remains unexplained by our models, which might be due to their linear character.
-Further attempts will have to be made in that regard.
+Additionally, we were able to show how the *rate* at which policy-compliance decreases differs across European countries.
 

### 2021-01-05 Draft.Rmd
Re-included plot on non-hierarchical model predictions and excluded mathematical formula

@@
 Interestingly, some of the coefficients for individual countries are not significant anymore when controlling for public attention and COVID-19 cases.
-In the following, a random intercept will be included for country, in order to improve model fit.
 
@@
 ## Linear Multi-Level Model
+The following plot visualizes the different intercepts, predicted by the non-hierarchical model.
+Along with the regression output of our non-hierarchical model, the fixed effects estimated for the different expressions of our country variable show substantial differences, with Germany showing more than 10 points less policy-compliance than our reference country Austria.
+In addition, we can see that despite the relationships between Date and Compliance being negative for all countries, there are different slopes.
 
-As we can see in the regression output of our non-hierarchical model, the fixed effects estimated for the different expressions of our country variable show substantial differences, with Germany showing more than 10 points less policy-compliance than our reference country Austria.
+```{r Plot different intercepts and slopes, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center"}
+### Non-hierarchical model different intercepts and different slopes
+ggplot(data = augment(lm(data = data, 
+                         ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days)),
+       aes(x = Date, y = ComplianceIndex, color = CountryName))  +
+  geom_smooth(aes(y = .fitted), method = "lm", se = FALSE) +
+  xlab("Month") +
+  scale_x_date(breaks = date_breaks("3 months"),
+               labels = date_format("%b\n%Y")) +
+  scale_y_continuous(name = "Policy Compliance Index") +
+  theme(
+    axis.title.y = element_text(color = "black", size=12, vjust = 3),
+    axis.title.x = element_text(size=12, vjust = 0.5),
+    text=element_text(family="CMU Sans Serif"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
+    strip.background = element_rect(fill="white"),
+    plot.title = element_text(size = 11, face = "bold")
+  ) +
+  ggtitle(label = "Model Predictions for Policy Compliance in Europe Across Time",
+          subtitle = "Non-hierarchical Model")
 
-To better assess the trends of policy-compliance in Europe over time, we can create a hierarchical model, allowing both random intercepts for the subgroups of Country as our grouping variable and random slopes along the Date variable.
+```
 
-\begin{equation}
-{Compliance}_{ij} = {\beta}_0 + {\beta}_1 * {Date}_{ij} + {\beta}_2 * {Public Attention}_{ij} + {\beta}_3 * {Cases/(100,000 * 14 days)}_{ij} + {\beta}_{1j} * {Date} + {Country}_{0j} + {\epsilon}_{0ij}
-\end{equation}
+Thus, in the following, a random intercept will be included for country, as well as a random slope for Date, in order to estimate the rate of change in policy compliance in different countries.
+This yields the following formula in lme4-syntax with the following results.
+
+`ComplianceIndex ~ Date + Public Attention + Cases per 100,000 and 14 Days + (Date | Country)`
 

### 2021-02-05 Analysis.Rmd
Renamed files

--- 2021-01-05 Draft.Rmd
@@
 
-This analysis has shown that, interestingly, levels of compliance with mobility-reducing COVID-19-policies differ across selected European countries and that policy-compliance expresses an alarming, negative trend.
+This analysis has shown that, interestingly, levels of compliance with mobility-reducing COVID-19-policies differ across selected European countries and that policy-compliance expresses an alarming, negative trend, so that we can reject our Null-hypotheses.
 Additionally, we were able to show how the *rate* at which policy-compliance decreases differs across European countries.
